% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Nikola Špirić}
\address{Somborska 15\linebreak 21000 Novi Sad, Serbia}
\contacts{(+381)61 157-94-64\linebreak nikola.spiric.ns@gmail.com}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Software Engineer, Intern}{Apple Computer}{Summer 2004}
			iChat AV			
			\begin{itemize}
				\item Reduced time to render the user’s buddy list by 75\% by implementing prediction algorithm.
				\item Implemented iChat integration with OS X Spotlight Search by creating tool which extracts metadata from saved chat transcripts and provides metadata to a system-wide search database.
				\item Redesigned chat file format and implemented backwards compatibility for search.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Lead Student Ambassador}{Microsoft Corporation}{Fall 2003 -- Spring 2005}	
			\begin{itemize}
				\item Promoted to Lead Student Ambassador in Fall 2004; supervised 10 -- 15 Student Ambassadors.
				\item Created and taught Computer Science course, CSE 099: Software Design and Development.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Head Teaching Assistant}{University of Pennsylvania}{Fall 2001 -- Spring 2005}		
			\begin{itemize}
				\item Courses: Advanced Java III, Software Engineering, Mathematical Foundations of Computer Science I \& II.
				\item Promoted to Head TA in Fall 2004; led weekly meetings and supervised four other TAs.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Design Engineer, Intern}{Microsoft Corporation}{Summers 2001 -- 2003}
			Visual Studio Core (Summer 2003)		
			\begin{itemize}
				\item Implemented a user interface for the VS open file switcher (ctrl-tab) and extended it to tool windows.
				\item Created service to provide gradient across VS and VS add-ins. Optimized service via caching.
			\end{itemize}
			Programmer Productivity Research Center (Summers 2001, 2002)
			\begin{itemize}
				\item Built app to compute similarity of all methods in a code base; reduced time from $O(n^2)$ to $O(n\ log\ n)$. 
				\item Created test case generation tool which creates random XML docs from XML Schema.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Serbia, Novi Sad}{Faculty of Technical Sciences}{Fall 2009 -- May 2014}
			\begin{itemize}
				\item M.S.E. in Electrical and Computer Engineering,May 2014. GPA: 8.49/10
				\item B.S.E. in Electrical and Computer Engineering, May 2013.  GPA: 10/10
				\item Graduate \& Undergraduate Coursework: Mathematical Analysis I \& II, Algebra, Programming Languages and Data Structures, Fundamentals of Electrical Engineering, Computer Architecture, System Modeling and Simulation, Logic Design of Computer Systems, Object Oriented Programming, Operating Systems, Automatic Control Systems, Real Time System Programming, Probability and Stochastic Processes, Optimization Method, Databases, Fundamentals of Computer Networks, Fundamentals of DSP Architecture and Algorithms, Web Programming, Dedicated Computer Structure Design
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{Python servlet library} (20?? ). sscTODO https://github.com/spiricn/ssc
	                                \item \textbf{Python web based RPI LED strip controller} (20?? ). rpis TODO https://github.com/spiricn/rpis
	                                \item \textbf{Python web based RPi brewing temperature controller } (20?? ). Pybrewer TODO https://github.com/spiricn/PyBrewer
				\item \textbf{Android Unity Game} (20?? ). Minesweeper clone game written in C\# (Unity Engine), published on Playstore and Facebook.
				\item \textbf{Game Engine \& World  Editor} (2012 – 2014). C++98 OpenGL game engine with a GUI world editor written in Qt. Key features include: physics intercation (via PhysX engine), scripting (via Lua interpreter bindings), sky boxes, sound effects (SFML), heatmap terrain rendering, basic game UI, skeletal animation, particle effects, custom 3D model format, crepuscular godray shared effect,  diretional, point and spot lighting (via deferred shading).
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Additional Experience and Awards}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{Instructor (2003 – 2005):} Taught two full-credit Computer Science courses; average ratings of 4.8 out of 5.0.
				\item \textbf{Third Prize, Senior Design Projects:} Awarded 3rd prize for Synchronized Calendar project, out of 100 projects.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item C++; C; Java; Objective-C; C\#.NET; SQL; JavaScript; XSLT; XML (XSD) Schema 
				\item Visual Studio; Microsoft SQL Server; Eclipse; XCode; Interface Builder
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}
